---
title: "Berlin Airbnb Analysis"
author: "Eric Jonas, Pavlo Kravets, Simon Schäfer, Florian Tilliet"
date: "`r Sys.Date()`"
output: 
  bookdown::gitbook:
    css: "custom.css"
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("../code/setup.R")

full_refit = F
```

# Introduction
Airbnb is a leading online marketplace that connects homeowners with individuals seeking temporary accommodations. It operates in over 220 countries and regions, making it a global player in the hospitality industry.

Examining the factors influencing Airbnb characteristics, such as prices, is particularly interesting because these are shaped by a variety of factors like location, seasonality and local events. Understanding these influences can provide valuable insights to find the best deals for an apartment and reveal a broader impact of external factors on Airbnb accommodations. Our report will focus on [Airbnb data](https://insideairbnb.com/get-the-data/) from Berlin for the years 2023 and 2024.


```{r templateFigure, echo=FALSE, message=FALSE, warning=FALSE, cache=!full_refit, fig.cap="Template", fig.align='center'}

```


## Data Description


## Objectives

